---
title: "Hello R"
author: "Kristen Blessman-Garcia"
date: "Data 2401"
output: html_document 
  
---
---



### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1
```{r}
datasaurus_dozen %>%
  count(dataset) %>%
  print(13)
```

A data frame with 1846 rows and 3 variables:

  dataset: indicates which dataset the data are from

  x: x-values

  y: y-values


  

### Exercise 2
Below is the plot for dino_data:

```{r plot-dino, fig.height=4, fig.width=3}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Below is the correlation between x and y for dino_data:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

Below is the plot of the star_data:



```{r plot-star, fig.height=4, fig.width=4}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Below is the correlation coefficient between x and y for this star dataset.
 
```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```

### Exercise 4

Below is the plot of the circle_data:

```{r plot-circle, fig.height=4, fig.width=3}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()

```

Below is the correlation data between x and y for circle_data:
 Notice that the correlation coefficient for the circle is .0038 smaller than for the dino.
 There is a .0053 difference between the star and circle.
 
```{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))
```

### Exercise 5

Below is a plot of all datasets at once with a calculation of their summary correlation coefficients:  Please see difference

```{r fig.height=8, fig.width=8}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
  geom_point()+
  facet_wrap(~ dataset, ncol = 3) +
  theme(legend.position = "none")

datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
  print(13)
```
